MSSM-Penn-Pitt - ACC and DLPFC - DREAM - SALMON - GRCh38 - Model Selection

### 2020-04-05 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_SALMON_GRCh38.Rmd
counts as df

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 salmon counts (ACC and DLPFC)';

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='compute-salmon')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21869686'
ALL_USED_IDs = counts
counts = readRDS(synGet(counts)$path)
counts = counts$counts

>>>>

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn21435176';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 salmon counts (ACC and DLPFC)';

@@

# Github link
thisRepo <- getRepo(repository = "kelshmo/analysis", ref="branch", refName='compute-salmon')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('cmc-rnaseq-de/',thisFileName))
```
### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21869686'
ALL_USED_IDs = counts
counts = readRDS(synGet(counts)$path)
counts = counts$counts %>% 
  as.data.frame()
